---
title: "Data Science I Homework 1 - lzs2109"
author: "Louis Sharp"
date: "9/22/2021"
output: github_document
---

**Problem 1**

```{r, message = FALSE}
library(tidyverse)
hw1_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_character = c("Sphinx", "of", "black", "quartz", "judge", "my", "vow", 
                    "is", "a", "pangram"),
  vec_factor = factor(c("good", "poor", "good", "good", "fair", "poor", "fair", 
                        "fair", "poor", "good"))
)

mean(pull(hw1_df, vec_numeric))
mean(pull(hw1_df, vec_logical))
mean(pull(hw1_df, vec_character)) #unable to take the mean of vec_character
mean(pull(hw1_df, vec_factor)) #also unable to take the mean of vec_factor
```

The character and factor vectors create an error when passing them through the mean
function, because a mean cannot be taken from characters. The result is NA. 
The logical vector is able to produce a mean, because a TRUE is equal to 1 and a 
FALSE is equal to 0. Passing logical vectors through the as.numeric function produces 
these 1s and 0s, as shown below. However, passing the character vectors forces all
entries to NAs, because no equivalent numeric values exist for characters and
words as far as R is concerned. This explains why R is unable to take the mean
of a character vector as well, as NA has no values to take the mean of. The mean
of a string of NAs will be NA. The factor vector however, since it has 'levels'
is converted to a number that represents its level when passed through the as.numeric
function, and a mean is now able to be taken from these level numbers.

```{r, eval = FALSE}
as.numeric(pull(hw1_df, vec_logical))
as.numeric(pull(hw1_df, vec_character))
as.numeric(pull(hw1_df, vec_factor))
mean(as.numeric(pull(hw1_df, vec_character)))
mean(as.numeric(pull(hw1_df, vec_factor)))
```

**Problem 2**

```{r}
data("penguins", package = "palmerpenguins") #loads in penguin dataset
```

The penguins dataset includes descriptive information about penguins! Information
about their habitat and variables describing body and appendage size as well as
sex and species are included in the dataset. The variables listed
in the dataset include `r names(penguins)`, for a total of `r ncol(penguins)`
rows and `r nrow(penguins)` observations, or different penguins. The word 
penguin is already starting to lose meaning from repetition. Interestingly, in
this dataset, the mean flipper length in millimeters 
is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm. Here's a scatterplot
of flipper length vs bill length! (both measured in millimeters)

```{r}
#plot penguins data below - flipper length vs bill length, colored by species
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, 
                     color = species)) + geom_point()

ggsave("penguin_plot.pdf") #saved plot to to project directory
```