---
title: "Data Science I Homework 1 - lzs2109"
author: "Louis Sharp"
date: "9/22/2021"
output: github_document
---

**Problem 1**

```{r, message = FALSE}
library(tidyverse)
hw1_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_character = c("I", "hope", "I'll", "do", "well", "during", "my", 
                    "studies", "in", "school"),
  vec_factor = factor(c("good", "fair", "poor", "fair", "fair", "good", "poor", "poor",
                 "fair", "good"))
)

mean(pull(hw1_df, vec_numeric))
mean(pull(hw1_df, vec_logical))
mean(pull(hw1_df, vec_character)) #unable to take the mean of vec_character
mean(pull(hw1_df, vec_factor)) #also unable to take the mean of vec_factor
```

The character vectors create an error when passing them through the mean
function, because a mean cannot be taken from characters. The logical vector
is able to produce a mean, because a TRUE is equal to 1 and a FALSE is equal
to 0. Passing logical vectors through the as.numeric function produces these
1s and 0s, as shown below. However, passing character vectors forces all
entries to NAs, because no equivalent numeric values exist for characters and
words as far as R is concerned. This explains why R is unable to take the mean
of a character vector as well, as NA has no values to take the mean of. The mean
of a string of NAs will be NA.

```{r, eval = FALSE}
as.numeric(hw1_df$vec_logical)
as.numeric(hw1_df$vec_character)
as.numeric(hw1_df$vec_factor)
mean(as.numeric(hw1_df$vec_character))
```

**Problem 2**

```{r}
data("penguins", package = "palmerpenguins")
```

The penguins dataset includes information about penguins! The variables listed
in the dataset include `r names(penguins)`, for a total of `r ncol(penguins)`
rows and `r nrow(penguins)` observations, or different penguins. The word 
penguin is already starting to lose meaning from repetition. Interestingly, in
this dataset, the mean flipper length in millimeters 
is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm. Here's a scatterplot
of flipper length vs bill length! (both measured in millimeters)

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, 
                     color = species)) + geom_point()

ggsave("penguin_plot.pdf")
```